The Strong Gravitational Lens Finding Challenge

### 2018-01-27 paper.tex
Update on Overleaf.

\begin{figure}
  \centering
      \includegraphics[width=1\columnwidth]{figures/Fig1_gamoclass.pdf} 
  \caption{GAMOCLASS schematic}
 \label{Fig1_gamoclass}
\end{figure}

@@

\section*{Acknowledgements}
AS was supported by World Premier International Research Center Initiative (WPI Initiative), MEXT, Japan.
RBM's research was partly part of project GLENCO, funded under the European Seventh Framework Programme, Ideas, Grant Agreement n. 259349.
AT acknowledges receipt of an STFC postdoctoral research
assistantship.
We thank the International Space Science Institute (ISSI) for hosting and funding our workshop.\footnote{http://www.issibern.ch/}
JPK and CS acknowledge support from the ERC advanced grant LIDA and the ESA-NPI grant 491-2016.
CA acknowledges support from the Enrico Fermi
Institute at the University of Chicago, and the University of Chicago
Provost's Office. NL would like to thank the funding support from
NSFC, grant no.11503064, and Shanghai Natural Science Foundation,
grant no. 15ZR1446700. This work was also supported in part by the
Kavli Institute for Cosmological Physics at the University of Chicago
through grant NSF PHY-1125897 and an endowment from the Kavli
Foundation and its founder Fred Kavli.

>>>>

\begin{figure*}
  \centering
      \includegraphics[width=1\textwidth]{figures/Fig1_gamoclass.pdf} 
  \caption{GAMOCLASS schematic}
 \label{Fig1_gamoclass}
\end{figure*}

@@

\section*{Acknowledgements}
AS was supported by World Premier International Research Center Initiative (WPI Initiative), MEXT, Japan.
RBM's research was partly part of project GLENCO, funded under the European Seventh Framework Programme, Ideas, Grant Agreement n. 259349. AT acknowledges receipt of an STFC postdoctoral research
assistantship.
We thank the International Space Science Institute (ISSI) for hosting and funding our workshop.\footnote{http://www.issibern.ch/}
JPK and CS acknowledge support from the ERC advanced grant LIDA and the ESA-NPI grant 491-2016.
CA acknowledges support from the Enrico Fermi
Institute at the University of Chicago, and the University of Chicago
Provost's Office. NL would like to thank the funding support from
NSFC, grant no.11503064, and Shanghai Natural Science Foundation,
grant no. 15ZR1446700. This work was also supported in part by the
Kavli Institute for Cosmological Physics at the University of Chicago
through grant NSF PHY-1125897 and an endowment from the Kavli
Foundation and its founder Fred Kavli. LVEK, CEP, CT and GV are supported through an NWO-VICI grant (project number 639.043.308). GVK acknowledges
financial support from the Netherlands Research School for
Astronomy (NOVA) and Target. Target is supported by
Samenwerkingsverband Noord Nederland, European fund for regional
development, Dutch Ministry of economic affairs, Pieken in de
Delta, Provinces of Groningen and Drenthe.
